Report for Tissue-Specific Proteins

### 2021-08-12 Tissue Specific Report.Rmd
comparing to full dataset instead of non-secreted tissue-specific

@@

r.squared_brain_notts = fin.r.squared_brain[!(fin.r.squared_brain$names_brain %in% colnames(ts_protein_brain)),]
r.squared_liver_notts = fin.r.squared_liver[!(fin.r.squared_liver$names_liver %in% colnames(ts_protein_liver)),]

@@

gee = cbind(rep("not ts", times = dim(r.squared_brain_notts)[1]), r.squared_brain_notts[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_brain_ts)[1]), r.squared_brain_ts[,2])

@@

gee = cbind(rep("not ts", times = dim(r.squared_liver_notts)[1]), r.squared_liver_notts[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_liver_ts)[1]), r.squared_liver_ts[,2])

@@

boxplot(fin.r.squared_brain[,2], r.squared_brain_ts[,2], names = c("Not TS", "TS"), xlab = "R Squared", main = "R Squared Brain Data")
boxplot(fin.r.squared_liver[,2], r.squared_liver_ts[,2], names = c("Not TS", "TS"), xlab = "R Squared", main = "R Squared Liver Data")

>>>>

## Tissue Specific Non-Secreted
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
#notsec_brain = read.csv("NotSecreted_Brain.csv")
#notsec_liver = read.csv("NotSecreted_Liver.csv")
#notsec_liver = fix.read.csv(notsec_liver)
#notsec_brain = fix.read.csv(notsec_brain)

#genes_brain = colnames(notsec_brain)
#genes_liver = colnames(notsec_liver)

#gee = genes_brain %in% genes_liver
#gee = gee == FALSE
#only_brain = genes_brain[gee]

#wee = genes_liver %in% genes_brain
#wee = wee == FALSE
#only_liver = genes_liver[wee]

#tsns_protein_brain = notsec_brain[, colnames(notsec_brain) %in% only_brain]
#tsns_protein_liver = notsec_liver[, colnames(notsec_liver) %in% only_liver]

#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
#write.csv(tsns_protein_brain, "NSTissueSpecific_Protein_Brain.csv")
#write.csv(tsns_protein_liver, "NSTissueSpecific_Protein_Liver.csv")

#sum(colnames(ts_protein_liver) %in% colnames(tsns_protein_liver))

@@

#r.squared_brain_notts = fin.r.squared_brain[!(fin.r.squared_brain$names_brain %in% colnames(ts_protein_brain)),]
#r.squared_liver_notts = fin.r.squared_liver[!(fin.r.squared_liver$names_liver %in% colnames(ts_protein_liver)),]

@@

gee = cbind(rep("full", times = dim(fin.r.squared_brain)[1]), fin.r.squared_brain[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_brain_ts)[1]), r.squared_brain_ts[,2])

@@

gee = cbind(rep("full", times = dim(fin.r.squared_liver)[1]), fin.r.squared_liver[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_liver_ts)[1]), r.squared_liver_ts[,2])

@@

boxplot(fin.r.squared_brain[,2], r.squared_brain_ts[,2], names = c("Full", "TS"), xlab = "R Squared", main = "R Squared Brain Data")
boxplot(fin.r.squared_liver[,2], r.squared_liver_ts[,2], names = c("Full", "TS"), xlab = "R Squared", main = "R Squared Liver Data")
